Natural selection in the Health and Retirement Study

### 2023-11-30 hrs-selection.qmd
Update renv

|               | Low group             | High group            | Difference            |
|------------------|------------------|------------------|------------------|
| Education     | `r tbl$edu[1]`        | `r tbl$edu[2]`        | `r tbl$edu[3]`        |
| Income        | `r tbl$income_med[1]` | `r tbl$income_med[2]` | `r tbl$income_med[3]` |
| Marriage      | `r tbl$married[1]`    | `r tbl$married[2]`    | `r tbl$married[3]`    |
| Age 1st birth | `r tbl$agefb[1]`      | `r tbl$agefb[2]`      | `r tbl$agefb[3]`      |
| Birth year    | `r tbl$born[1]`       | `r tbl$born[2]`       | `r tbl$born[3]`       |

>>>>

|               | Low group             | High group            | Difference            |
|---------------|-----------------------|-----------------------|-----------------------|
| Education     | `r tbl$edu[1]`        | `r tbl$edu[2]`        | `r tbl$edu[3]`        |
| Income        | `r tbl$income_med[1]` | `r tbl$income_med[2]` | `r tbl$income_med[3]` |
| Marriage      | `r tbl$married[1]`    | `r tbl$married[2]`    | `r tbl$married[3]`    |
| Age 1st birth | `r tbl$agefb[1]`      | `r tbl$agefb[2]`      | `r tbl$agefb[3]`      |
| Birth year    | `r tbl$born[1]`       | `r tbl$born[2]`       | `r tbl$born[3]`       |
